Geometric models reveal behavioral and neural signatures of transforming experiences into memories

### 2020-10-22 paper/main.tex
replaced data and code hyperlinks in with urls

\section*{Data availability}
The fMRI data we analyzed are available online \href{http://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179}{\underline{here}}.  The behavioral data is available  \href{https://github.com/ContextLab/sherlock-topic-model-paper}{\underline{here}}.

\section*{Code availability}
All of our analysis code may be downloaded \href{https://github.com/ContextLab/sherlock-topic-model-paper}{\underline{here}}.

>>>>

\section*{Data availability}
The fMRI data we analyzed are available online at:

https://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179

\noindent The behavioral data is available at:

https://github.com/ContextLab/sherlock-topic-model-paper/tree/master/data/raw

\section*{Code availability}
All of our analysis code may be downloaded from:

https://github.com/ContextLab/sherlock-topic-model-paper
